### 2016-05-03 article.tex
begin to translate article to russian
merge

Thus, each application can be represented as a tuple:
\begin{equation}
\forall q \in Q: \exists q = (s_q,r_q, \vec{P}_{s_q}, \vec{P}_{r_q}, w_q, t_{s}^{q}, \Delta{t_{s}^{q}}, t_{r}^{q}, \Delta{t_{r}^{q}})
\end{equation}
To estimate the cost of transportation between destinations defined cost function $\Omega$:
\begin{equation}
\forall i,j \in S \cup R: \exists \Omega_{i,j} = \Omega(\vec{P}_i,\vec{P}_j)
\end{equation}

@@

The algorithm terminates at a local optimum, when $F(\vec{x^{i+1}})=F(\vec{x^i})$. When solving the transportation problem is a typical situation when many local optimums and only one of them is global:
\begin{align} 
& F_{opt}=min\{F(\vec{v}):v \in E^{\eta}\}
\end{align}

@@

As a result the client $u^*$ is added to the current route $k$ the position between nodes $v_i$ and $v_i+1$.

@@

As should have been expected, for large values of the parameter a jam occurs in local optimum due to the large number of restrictions of movement in space. Otherwise if you select a too small tabu size, algorithm can still get stuck in a local optimum. In the first computational experiment we made finding the best solutions for different values of the tabu size parameter from interval $h \in [0, 40]$ (pict. \ref{aba:fig2} an pict. \ref{aba:fig3}).
\begin{figure}[h]
	\hfil\includegraphics[height=2.2in]{images/tabuSize_time}\hfil
	\caption
	{
	  The dependence of the quality of solutions on the size of the tabu list when using $ TimeSpent $ termination strategy
	}
	\label{aba:fig3}
\end{figure}

\begin{figure}[h]
	\hfil\includegraphics[height=2.2in]{images/acceptedCountLimit}\hfil
	\caption
	{
	  The dependence of the quality of solutions on the neighborhood size when using $ TimeSpent $ termination strategy
	}
	\label{aba:fig4}
\end{figure}

@@

\bibitem{Goldberg_Kennedy} V.~Goldberg, R.~Kennedy, An Efficient cost scaling algotirhm for the assignment problem, Math. Program., 1995, p. 153--177.

>>>>

Thus, each request can be represented as a tuple:
\begin{equation}
\forall q \in Q: q = (s_q,r_q, \vec{P}_{s_q}, \vec{P}_{r_q}, w_q, t_{s}^{q}, \Delta{t_{s}^{q}}, t_{r}^{q}, \Delta{t_{r}^{q}})
\end{equation}
To estimate the cost of transportation between destinations defined cost function $\Omega$:
\begin{equation}
\forall i,j \in S \cup R: \exists \Omega_{i,j} = \Omega(\vec{P}_i,\vec{P}_j)
\end{equation}

@@

The algorithm terminates at a local optimum, when $F(\vec{u^{i+1}})=F(\vec{u^i})$. When solving the transportation problem is a typical situation when many local optimums and only one of them is global:
\begin{align} 
& F_{opt}=min\{F(\vec{v}):v \in E^{\eta}\}
\end{align}

@@

As a result the client $u^*$ is added to the current route $k$ the position between nodes $v_i$ and $v_(i+1)$.

@@

As should have been expected, for large values of the parameter a jam occurs in local optimum due to the large number of restrictions of movement in space. Otherwise if you select a too small tabu size, algorithm can still get stuck in a local optimum. In the first computational experiment we made finding the best solutions for different values of the tabu size parameter from interval $h \in [0, 40]$ (pict. \ref{aba:fig2} an pict. \ref{aba:fig3}).
\begin{figure}[h]
	\hfil\includegraphics[height=2.2in]{images/tabuSize_time}\hfil
	\caption{
	  The dependence of the quality of solutions on the size of the tabu list when using $ TimeSpent $ termination strategy
	}
	\label{aba:fig3}
\end{figure}

\begin{figure}[h]
	\hfil\includegraphics[height=2.2in]{images/acceptedCountLimit}\hfil
	\caption{
	  The dependence of the quality of solutions on the neighborhood size when using $ TimeSpent $ termination strategy
	}

	\label{aba:fig4}
\end{figure}

@@

\bibitem{Goldberg_Kennedy} V.~Goldberg, R.~Kennedy, An Efficient cost scaling algorithm for the assignment problem, Math. Program., 1995, p. 153--177.
